DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-02-01 paper/intro.tex
video links

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We provide the design and implementation of a low-cost
    autonomous car testbed, DeepPicar, which is based on a
    state-of-the-art end-to-end deep learning, as
    open-source~\footnote{The source code, build 
instruction, and a collection of self-driving videos of the DeepPicar
can be found at: \url{https://github.com/heechul/picar}}, with the
    goal of lowering the economic and safety-related barriers to study
    autonomous cars.

>>>>

% contributions
The {\bf contributions} of this paper are as follows:
\begin{itemize}
  \item We provide the design and implementation of a low-cost
    autonomous car testbed, DeepPicar, which is based on a
    state-of-the-art end-to-end deep learning, as
    open-source~\footnote{The source code, build 
instruction the DeepPicar
can be found at: \url{https://github.com/heechul/picar}}, with the
    goal of lowering the economic and safety-related barriers to study
    autonomous cars.
